An Examination of Sport Climbing Competition Format and Scoring System

### 2021-07-30 manuscript/Rmd/draft.Rmd
Bed time

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE,
                      comment = "",
                      fig.height = 4,
                      fig.width = 5,
                      results = "asis")
options(xtable.comment = FALSE,
        xtable.caption.placement = "top", 
        xtable.include.rownames = FALSE)
```

@@

>>>>

```{r setup, include=FALSE}
# install.packages(c("rticles", "xtable", "GGally", "patchwork", "cowplot"))
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE,
                      comment = "",
                      fig.height = 4,
                      fig.width = 5,
                      results = "asis")
options(xtable.comment = FALSE,
        xtable.caption.placement = "top", 
        xtable.include.rownames = FALSE)
```

@@

# Supplementary Material {-}

All of the materials related to this manuscript are publicly available on GitHub at \newline https://github.com/qntkhvn/climbing.
